\TheTitle

### 2016-04-24 linvis.tex
small commit, more needs to be done

\dmg{I am going to describe the method we used here... }

German et al. recorded the metadata of every commit and merge in the Linux git
repository starting in 2011 \cite{German2015}, including chronological data that is
not stored by git. We are able to use this information to determine when a commit
has been merged into the kernel, regardless of rebases preceding and proceeding that
point in time. This information is then converted by a heuristic method, described
by German, to generate sets of trees, which we use as our core model instead of
using the DAG. Each tree is rooted by the top-level merge performed by Linus, which
merges the branches or a set of commits into the kernel.

In this paper, we present our design decisions behind a web-based
tool\footnote{\url{http://li.turingmachine.org}} built around the tree-based model
instead of the DAG. Our tool provides information about the location of a given
commit in the respective merge tree, the files edited, the modules edited, and the
commit message for a given commit or merge. The tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

>>>>

% \dmg{I am going to describe the method we used here... }

% German et al. recorded the metadata of every commit and merge in the Linux git
% repository starting in 2011 \cite{German2015}, including chronological data that is
% not stored by git. We are able to use this information to determine when a commit
% has been merged into the kernel, regardless of rebases preceding and proceeding that
% point in time. This information is then converted by a heuristic method, described
% by German, to generate sets of trees, which we use as our core model instead of
% using the DAG. Each tree is rooted by the top-level merge performed by Linus, which
% merges the branches or a set of commits into the kernel.

 The contributions of this paper are two. First, we describe a method to convert the DAG of the Linux repository into a tree (we call this the tree model of the
 reposisory) that represents the path used by
 any commit to reach master. Second, 
 we present a method to inspect and visualize the history of merges in the  Linux project using the tree-model of the repository

These methods and visualizations have been implemented in a web-based
tool\footnote{It is currently available at \url{http://li.turingmachine.org}}
instead of the DAG. Our visualizations and tool provide information about the location of any given
commit in the respective merge tree, the files edited, the modules edited, and the
commit message for a given commit or merge. Our tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

\evantodo{move to discussion}
